Capstone Movielens Report

### 2025-11-18 reports/capstone-movielens.site/05.appendix.Rmd
Fixes for functions` descriptions: `tune.model_param` ,`model.tune.param_range`.

We call this function internally from the functions that compute the _penalized estimates_  as described in section [Section 24.1 *Case study: recommendation systems / Penalized Least Squares*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#penalized-least-squares) of the _Course Textbook (New Edition)_[@IDS2_24-1].

@@

Implements an algorithm to find a value of the *regularization parameter* $\lambda$ that corresponds to the minimum value of the *Root Mean Squared Error (RMSE)* for the model under test (we call this the *best value of the regularization parameter* or *best value of $\lambda$*) from the sorted *parameter vector* passed in the [param_values](#func.tune.model_param.args.param_values) argument.

@@

The algorithm iterates through the $\lambda$ parameter values from the list passed in the [param_values](#func.tune.model_param.args.param_values) argument, computing the model's *RMSE* for each of them, using the helper function specified by the [fn_tune.test.param_value](#func.tune.model_param.args.fn_tune.test.param_value) argument.

@@

Implements an algorithm for fine-tuning the model under test by finding the most precise value possible of the *regularization parameter* $\lambda$ that corresponds to the minimum value of the *Root Mean Squared Error (RMSE)* (we call this the *best value of the regularization parameter* or *best value of $\lambda$*) over a given interval determined by the start and end values of the interval passed in the [loop_starter] argument.

@@

::: { #func.model.tune.param_range.details .sidebar }
##### **Details** 
\
During execution, the algorithm organizes a cycle consisting of the following steps:

>>>>

We call this function internally from the functions that compute the _penalized estimates_  as described in [Section 24.1 *Case study: recommendation systems / Penalized Least Squares*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#penalized-least-squares) of the *Course Textbook (New Edition)*[@IDS2_24-1].

@@

Implements an algorithm for selecting the best value of the *regularization parameter* $\lambda$ from the sorted *parameter vector* passed in the [param_values](#func.tune.model_param.args.param_values) argument, using the *penalized approach* to regularize predictions as explained in [Section 24.1 *Case study: recommendation systems / A penalized approach](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#a-penalized-approach) of the *Course Textbook (New Edition)*[@IDS2_24-1].

@@

With the approach used in this algorithm, the best value of the *regularization parameter* $\lambda$ (we call this the *best value of the regularization parameter* or the *best value of $\lambda$*) is considered to be the value corresponding to the minimum value of the *Root Mean Square Error (RMSE)* for the model being tested.

To find the best value of the $\lambda$ parameter, the algorithm iterates over the values from the list passed in the [param_values](#func.tune.model_param.args.param_values) argument, computing the *RMSE* of the model for each of them, using the helper function specified in the [fn_tune.test.param_value](#func.tune.model_param.args.fn_tune.test.param_value) argument.

@@

Implements an algorithm for fine-tuning the model under test by figuring out the most precise value possible of the *regularization parameter* $\lambda$ over a given interval determined by the start and end values of the interval passed in the [loop_starter] argument, using the *penalized approach* to regularize predictions as explained in [Section 24.1 *Case study: recommendation systems / A penalized approach](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#a-penalized-approach) of the *Course Textbook (New Edition)*[@IDS2_24-1].

@@

::: { #func.model.tune.param_range.details .sidebar }
##### **Details** 
\

With the approach used in this algorithm, the best value of the *regularization parameter* $\lambda$ (we call this the *best value of the regularization parameter* or the *best value of $\lambda$*) is considered to be the value corresponding to the minimum value of the *Root Mean Square Error (RMSE)* for the model being tested.

During the execution, the algorithm organizes a cycle consisting of the following steps:
